Modal Abstractions for Virtualizing Memory Addresses

### 2023-08-13 examples.tex
remove line about inconsistency with fpaddr since that was fixed
+

\lstset{
  columns=fullflexible,
  numbers=left,
  basicstyle=\ttfamily,
  keywordstyle=\color{blue}\bfseries,
  morekeywords={mov,add,call},
  emph={rsp,rdx,rax,rbx,rbp,rsi,rdi,rcx,r8,r9,r10,r11,r12,r13,r14,r15},
  emphstyle=\color{green},
  emph={[2]cr3},
  emphstyle={[2]\color{violet}},
  morecomment=[l]{;;},
  mathescape
}

@@

mov %r14, %rax ;; Save that before another call

@@

mov (%r14), %rax

@@

At this point in the proof,  $\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr})$ 
contains  full ownerhsip of the L1 table entry physical pointsto $\paddr
\mapsto_{\mathsf{p}} \textsf{fpaddr}$ . Then, we can split the full-ownership of that
physical pointsto
($\textsf{fpaddr}\mapsto_{\textsf{p}} \;\textsf{wzero 64}$) to obtain
fractional ownership on it appropriate for a single address's share of an L1 entry (q4).
Since we know $\texttt{addr\_L1 }(\vaddr,
\entryo) \mapsto_{\mathsf{p}} \{q4\} \;\textsf{fpaddr}$) from
$\mapsto_{\textsf{vpte}}$, after the split of the PTE points-to, we can
connect L4-L2 points-to assertions (in Specification Lines 24 and 25) with 
 $\texttt{fpaddr} \mapsto_{a} (\texttt{wzero 64})$ to obtain the
complete physical table-walk assertion (L4\_L1\_PointsTo($\vaddr$ l4e l3e l2e
fpaddr)) in Line 30. Reaching right at this point in the specification, we must note that we did find a trivial inconsistency in the postcondition related to conflating fpaddr as an address with the page table entry that reference fpaddr, and while the fix is straightforward we ran out of time.

@@

mov 0[%rdi], %rbx
mov 8[%rdi], %rsp
mov 16[%rdi], %rbp
mov 24[%rdi], %r12
mov 32[%rdi], %r13
mov 40[%rdi], %r14
mov 48[%rdi], %r15

@@

mov %rbx, 0[%rsi] 

@@

mov %rsp, 8[%rsi] 
mov %rbp, 16[%rsi]
mov %r12, 24[%rsi]
mov %r13, 32[%rsi]
mov %r14, 40[%rsi]
mov %r15, 48[%rsi]

@@

mov %cr3, 56[%rsi]

>>>>

%\lstset{
%  columns=fullflexible,
%  numbers=left,
%  basicstyle=\ttfamily,
%  keywordstyle=\color{blue}\bfseries,
%  morekeywords={mov,add,call},
%  emph={rsp,rdx,rax,rbx,rbp,rsi,rdi,rcx,r8,r9,r10,r11,r12,r13,r14,r15},
%  emphstyle=\color{green},
%  emph={[2]cr3},
%  emphstyle={[2]\color{violet}},
%  morecomment=[l]{;;},
%  mathescape

@@

mov r14, rax ;; Save that before another call

@@

mov [r14], rax

@@

At this point in the proof,  $\texttt{pte\_addr} \mapsto_{\texttt{vpte}}  \; \paddr\; \textsf{fpaddr})$ 
contains  full ownerhsip of the L1 table entry physical pointsto $\paddr
\mapsto_{\mathsf{p}} \textsf{fpaddr}$ . Then, we can split the full-ownership of that
physical pointsto
($\textsf{fpaddr}\mapsto_{\textsf{p}} \;\textsf{wzero 64}$) to obtain
fractional ownership on it appropriate for a single address's share of an L1 entry (q4).
Since we know $\texttt{addr\_L1 }(\vaddr,
\entryo) \mapsto_{\mathsf{p}} \{q4\} \;\textsf{fpaddr}$) from
$\mapsto_{\textsf{vpte}}$, after the split of the PTE points-to, we can
connect L4-L2 points-to assertions (in Specification Lines 24 and 25) with 
 $\texttt{fpaddr} \mapsto_{a} (\texttt{wzero 64})$ to obtain the
complete physical table-walk assertion (L4\_L1\_PointsTo($\vaddr$ l4e l3e l2e
fpaddr)) in Line 30.

@@

mov 0[rdi], rbx
mov 8[rdi], rsp
mov 16[rdi], rbp
mov 24[rdi], r12
mov 32[rdi], r13
mov 40[rdi], r14
mov 48[rdi], r15

@@

mov rbx, 0[rsi] 

@@

mov rsp, 8[rsi] 
mov rbp, 16[rsi]
mov r12, 24[rsi]
mov r13, 32[rsi]
mov r14, 40[rsi]
mov r15, 48[rsi]

@@

mov cr3, 56[rsi]
